Verification of a TCP/IP stack

### 2021-05-12 SecDev21/Automaton.tex
First draft of the paper

\begin{figure}[t]
{\centering\scalebox{.7}{
\begin{tikzpicture}[>=latex]
    \def\tfrac#1#2{\ensuremath{\displaystyle\frac{\text{\footnotesize#1}}{\text{\footnotesize#2}}}}
    %
    % Styles for states, and state edges
    %
    \tikzstyle{state} = [draw, very thick, fill=white, rectangle, minimum height=3em, minimum width=7em, node distance=8em, font={\sffamily\bfseries}]
    \tikzstyle{stateEdgePortion} = [black,thick];
    \tikzstyle{stateEdge} = [stateEdgePortion,->];
    \tikzstyle{edgeLabel} = [pos=0.5, text centered, font={\sffamily\small}];

    %
    % Position States
    %
    \node[state, name=closedStart] {CLOSED};
    \node[state, name=listen, below of=closedStart] {LISTEN};
    \node[state, name=synSent, below of=listen, right of=listen, xshift=8em] {SYN\_SENT};
    \node[state, name=synRcvd, below of=listen, left of=listen, xshift=-8em] {SYN\_RCVD};
    \node[state, name=established, below of=listen, node distance=14em] {ESTABLISHED};
    \node[state, name=finWait1, below of=established, left of=established, node distance=7em, xshift=-9em] {FIN\_WAIT\_1};
    \node[state, name=finWait2, below of=finWait1] {FIN\_WAIT\_2};
    \node[state, name=closeWait, below of=established, right of=established, node distance=7em, xshift=9em] {CLOSE\_WAIT};
    \node[state, name=closing, below of=established, node distance=14em] {CLOSING};
    \node[state, name=lastAck, below of=closeWait] {LAST\_ACK};
    \node[state, name=timeWait, below of=closing] {TIME\_WAIT};

>>>>

\begin{figure}[t]
    {\centering\scalebox{.55}{
    \begin{tikzpicture}[>=latex]
        \def\tfrac#1#2{\ensuremath{\displaystyle\frac{\text{\small#1}}{\text{\small#2}}}}
        %
        % Styles for states, and state edges
        %
        \tikzstyle{state} = [draw, very thick, fill=white, rectangle, minimum height=3em, minimum width=7em, node distance=8em, font={\sffamily\bfseries}]
        \tikzstyle{stateEdgePortion} = [black,thick];
        \tikzstyle{stateEdge} = [stateEdgePortion,->];
        \tikzstyle{edgeLabel} = [pos=0.5, text centered, font={\sffamily\small}];

        %
        % Position States
        %
        \node[state, name=closedStart] {CLOSED};
        \node[state, name=listen, below of=closedStart] {LISTEN};
        \node[state, name=synSent, below of=listen, right of=listen, xshift=8em] {SYN-SENT};
        \node[state, name=synRcvd, below of=listen, left of=listen, xshift=-8em] {SYN-RCVD};
        \node[state, name=established, below of=listen, node distance=14em] {ESTABLISHED};
        \node[state, name=finWait1, below of=established, left of=established, node distance=7em, xshift=-9em] {FIN-WAIT-1};
        \node[state, name=finWait2, below of=finWait1] {FIN-WAIT-2};
        \node[state, name=closeWait, below of=established, right of=established, node distance=7em, xshift=9em] {CLOSE-WAIT};
        \node[state, name=closing, below of=established, node distance=14em] {CLOSING};
        \node[state, name=lastAck, below of=closeWait] {LAST-ACK};
        \node[state, name=timeWait, below of=closing] {TIME-WAIT};
